TBD

### 2021-03-12 outputs/paper/paper.Rmd
123

## missing value
```{r missing, fig.cap="Missing value Visualization ", echo=FALSE, fig.width=10, fig.height=10}
library("VIM")
aggr(dat,prop=FALSE,numbers=TRUE)

>>>>

## missing value
```{r missing, fig.cap="Missing value Visualization ", echo=FALSE, fig.width=10, fig.height=10}

library("VIM")
aggr(dat,prop=FALSE,numbers=TRUE)
